Prefix-free graphs and suffix array construction in sublinear space

### 2023-06-22 manuscript/main.tex
finished iteration

>>>>

In the case of a singleton block with only a single occurence we need to report only a single suffix array entry.
Given the row index $i$, this entry can be calculated with the following equation:

\begin{equation}
    \label{eq:sa_entry}
    \texttt{SA entry} = \texttt{starts}[\texttt{ID}[i]] + \texttt{pos}[i]
\end{equation}

As an example, consider the row $13$ in the Suffix Table (\ref{tab:suffix}), the first row yielding a SA value.
It's segment ID is $0$ and from the Segment Table (\ref{tab:segment}) we see that there is only one occurence of segment $0$ and it starts at position $9$ in the pangenome.
The offset from the start of a segment $\texttt{pos}[13]$ is $0$.
This yields the first entry of a suffix array $9 + 0 = 9$ corresponding to the lexicographically smallest suffix $P[9..] = \texttt{ACACT}$.

The second, slightly more complex case is a singleton block with several occurences in the pangenome.
For this case, we need to report as many suffix array entries as the number of occurences.
Because the starting segment positions in the Segment Table (\ref{tab:segment}) are sorted based on their right context rank, we can iterate through these starting positions and apply Equation \ref{eq:sa_entry} to each of them.

As an example, consider the row $14$ in the Suffix Table (\ref{tab:suffix}).
This suffix occurs twice in the pangenome in segments starting at positions $15$ and $1$.
Since the offset from the start of a segment $\texttt{pos}[14]$ is $0$, we report a suffix array entry $15 + 0 = 15$ and $1 + 0 = 1$, corresponding to the suffixes $P[15..] = \texttt{ACGACT}$ and $P[1..] = \texttt{ACGTACT}$.

In the last case, we have a non-singleton block with suffixes of several segments, possibly with multiple occurences.
These suffixes represent the same substring of the original pangenome.
Here, we report a suffix array entry for each occurence of the substring in the pangenome.
To identify which entry is the first, we need to find the starting position with the smallest right context rank.
Because the ranks are sorted, this procedure is similar to the merging phase of a merge sort.
To iterate through all suffix array entries in the block, we therefore always identify the segment start with the next smallest right context rank and apply Equation \ref{eq:sa_entry} to this segment start.

As an example, consider the block at rows $[20..21]$ in the Suffix Table (\ref{tab:suffix}).
The relevant segment IDs are $0$ and $3$, with segment starts at positions $9$, $8$, $14$ and $0$.
The right context ranks from smallest to highest are $4, 5, 6, 9$ with the corresponding segment starts $8, 14, 0, 9$.
Applying Equation \ref{eq:sa_entry} to these segment starts yields a suffix array entries $8 + 0 = 8$, $14 + 0 = 14$, $0 + 0 = 0$ and $9 + 1 = 10$, representing pangenome suffixes $P[8..] = \texttt{CACACT}$, $P[14..] = \texttt{CACGACT}$, $P[0..] = \texttt{CACGTACT}$, and $P[10..] = \texttt{CACT}$.
